Hunting experience and prey variability jointly shape individual foraging specialisation in a predator-prey videogame

### 2022-08-16 manuscript/Chapter3-manuscript.Rmd
started the methods section

---
title: "Hunting experience and prey variability jointly shape individual foraging specialisation in a predator-prey videogame"
output: 
  word_document:
    reference_docx: Chapter3-styles.docx
bibliography: references.bib
csl: e-letters.csl
---

@@

@@

## The role of experience in the development of expertise

>>>>

---
title: "Hunting experience and prey variability jointly shape individual foraging specialisation in a predator-prey videogame"
output: 
  word_document:
    reference_docx: Chapter3-styles.docx
    fig_caption: yes
bibliography: references.bib
csl: e-letters.csl
---

```{r setup, include = FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

library(data.table)
library(brms)

```

@@

## Study system

## Data collection

## Behaviors

## Statistical analyses

### Software and computer components

### Effect of experience on hunting success

### Foraging tactics at each level of experience

@@

## Effect of experience on hunting success

Contrary to our predictions, individual predators did not differ in the development of their expertise, as the best model was the one with a general population trend with varying intercepts only (Table x.). Moreover, we did not detect a relationship between experience (i.e. the cumulative amount of matches played) and hunting success, such that players did not optimize their success with increasing experience as we expected (Figure 1 A). However, predators did differ in their average hunting success across the study period (Figure 1 B).

```{r out.width = "100%", fig.cap = "**Figure 1.** Results from the Bayesian generalized additive mixed model. (A) Fitted (solid) line displaying the posterior predicted values relating the predators' hunting success to their cumulative experience. Here, we transformed the hunting success and cumulative experience back to their original scale (i.e. the amount of prey captured and the number of matches played respectively). The band around the solid line represents the 95% credible intervals. (B) The estimated posterior predicted mean hunting success of each predator player. We display the hunting success back-transformed to its original scale."}
knitr::include_graphics(here::here("outputs", "05_outputs_figures", "05_figure1.png"))
```
